Dynamic Topic Modeling for Voice Dialogues

### 2024-04-22 paper/main.tex
fix ttile of paper + limitations

\title{Dynamic Topic Modeling for Voice Dialogues}
\author{Miakov Timofey Ilich}
\supervisor{Professor NRU HSE - Nizhniy Novgorodw}{L.V. Savchenko }
\Year{2024}
\Abstract{

}

@@

\section{Research Objectives}
The objectives of the thesis work are:
\begin{enumerate}
    \item Research of existing solutions for dynamic text and dialogue topic modelling
    \item The definition of the main stages for DTM for audio dialogues
    \item The identification of suitable training data sets and their collection
    \item An exploration of the possibilities of using large language models for some stages and the selection of models suitable for training in limited resources
    \item The development of the architecture of all stages and their interconnections
    \item Selection of appropriate metrics and measurement of the quality of the approaches used at each stage
    \item Visual analysis of the pipeline operation on pre-selected audio data
\end{enumerate}

@@

@@

\section{BERT}

@@

\section{Large Language models}

\subsection{LLaMA}

\subsection{Mistral}

@@

The dialogue segmentation stage represents the initial stage for textual type of data. 
The result is a set of utterance indices that indicate the beginning of a thematically related group.

@@

\subsection{Depth Scores calculation}

@@

@@

@@

>>>>

\title{Dynamic Topic Modeling for Voice Dialogues}
\author{Miakov Timofey Ilich}
\supervisor{Professor NRU HSE - Nizhniy Novgorod}{L.V. Savchenko}
\Year{2024}
\Abstract{}

@@

\section{Research Objectives}

The objectives of the thesis work are:
\begin{enumerate}
    \item Research of existing solutions for dynamic text and dialogue topic modelling
    \item The definition of the main stages for DTM for audio dialogues
    \item The identification of suitable training data sets and their collection
    \item An exploration of the possibilities of using large language models for some stages and the selection of models suitable for training in limited resources
    \item The development of the architecture of all stages and their interconnections
    \item Selection of appropriate metrics and measurement of the quality of the approaches used at each stage
    \item Visual analysis of the pipeline operation on pre-selected audio data
\end{enumerate}

@@

\subsection{LayerNorm}

%do it

@@

\section{BERT}
\subsection{Model overview}

@@

\section{Large Language Model Meta AI}

\section{Mistral LLM}

@@

\subsection{Utterance-Pair Coherence Scoring approach}
The dialogue segmentation stage represents the initial stage for textual type of data. 
The result is a set of utterance indices that indicate the beginning of a thematically related group.

@@

\subsection{Depth Scores}

@@

\subsection{Experiments settings}

@@

The input data at this stage are dialogues divided into separate utterances of the participants ${ut_1, ut_2, \dots, ut_n}$.

@@

\subsection{Topic Evolution}

\chapter{Limitations}

The LLM and other models require a significant amount of computing resources, including GPUs. Due to the limited availability of resources, the models were not larger than 8 billion parameters and did not exceed 16 GB during training and inference at all stages. 
Additionally, due to the lack of financial opportunities, open-source models were employed in the work. Should it be possible to reproduce all stages on more advanced models (such as GPT 4 or Lama 80b), the experimental results would be considerably more favourable.
